\section{Feedback}
\begin{quotation}%
  \itshape%
  \noindent%
  \begin{itemize}
    \item[1.1)] good  

    \item[2.1)] alright 

    \item[2.2)] good 

    \item[2.3)] good , adding plots would be more straightforward. 

    \item[2.4)]
      you miss the constraints for $x_vf$, and the constraint for all faces $f $is
      incorrect.  Moreover you should write is as a linear program.

    \item[2.5)]
      try to map the face to the vertex, let $a, b$ be the two vertexs, then $z_ab$,
      $z_ba$ should be the flows on the edges connected these two vertexs. the demand
      for vertex $b$ should be $z_{ba}-z_{ab}$, then show the sum of the demands in the graph
      is $0$

    \item[3.1)]
      Your reasoning fails due to your exponential function argument. This can be
      made much simpler by just considering an edge with capacity $(-\infty;\infty)$,
      and what sending flow back over an antiparallel edge entails (what about the
      case when an antiparallel edge already exists?). You should also explain why and
      optimal solution to the MCFP yields an optimal solution to GMCFP and if there is
      no solution in the former, there is not one in the latter, i.e. that they are
      equivalent. Please read the assignment text carefully for the resubmission.

    \item[3.2)] same

    \item[3.3)]
      No. Consider an edge $e$ with capacity $(l_e, u_e)$ where $l_e$ is negative. In
      general: Be more careful when you read the assignment text.
  \end{itemize}

  {\large \undernice{\textbf{Redo 3 to pass.}}}
\end{quotation}
--- Yiran Zhang

(We've re-done 3)
